Domain Specific Language for high performance computing

### 2024-02-05 paper/paper.tex
20240205

\subsection{AVX2 for parallelization}
To perform SIMD operations, just like with regular computations, data is first loaded from memory, computed based on that data,
and the results are stored. However, in the case of SIMD, computations are performed using SIMD-specific registers, so the 
methods of loading, computing, and storing differ. When loading, multiple elements that will undergo the same instruction are
stored in a SIMD-specific register. These are then used to perform computations simultaneously, and the results are stored for
each.

@@

\begin{lstlisting}[frame=single, caption=hoge]
//(1) include part
#include<math>
#include<immintrin.h>
int kernel( (2) double xi[][3], double xj[][3], double eps2 ...) {
  //(3) decleare tmp variable
  int i;
  int j;
  __m256d xi_tmp_v0;
  __m256d xi_tmp_v1;  
  __m256d xi_tmp_v2;
  __m256d eps2_tmp;
  . 
  .
  .

  // (4) loop increment
  for(i = 0;i < (n);i += 4) {
    // (5) Load EPI variable part and initialize result temporary variable
      int index_gather_0[4] = {0, 3, 6, 9};
      __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);
      .
      .
      .

    for(j = 0;j < (n);j += 1) {
      // (6) Load EPJ variable part
         xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
         xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
         xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);

      // (7) calculate interparticle
    }

    // (8) Store result part

  }
  return 0;
}

\end{lstlisting}

>>>>

\subsection{AVX2 for parallelization}
% _mm256dの説明はここですべきか？ codegen で説明すべきか
To perform SIMD operations, just like with regular computations, data is first loaded from memory, computed based on that data,
and the results are stored. However, in the case of SIMD, computations are performed using SIMD-specific registers, so the 
methods of loading, computing, and storing differ. When loading, multiple elements that will undergo the same instruction are
stored in a SIMD-specific register. These are then used to perform computations simultaneously, and the results are stored for
each.

@@

\begin{lstlisting}[frame=single, caption=hoge]
//(1) include part
#include<math>
#include<immintrin.h>
int kernel( (2) double xi[][3], double xj[][3], double eps2, double ai[][3], ...) {
  //(3) decleare tmp variable
  int i;
  int j;
  __m256d xi_tmp_v0;
  __m256d xi_tmp_v1;  
  __m256d xi_tmp_v2;
  __m256d eps2_tmp;
  // ... 
  // ... 
  // ... 
  //(4) def not class variables
  eps2_tmp = _mm256_set1_pd(eps2);
  // ... 
  // ... 
  // ...

  // (5) loop increment
  for(i = 0;i < (n);i += 4) {
    // (6) Load EPI variable part
    int index_gather_0[4] = {0, 3, 6, 9};
    __m128i vindex_gather_0 = _mm_load_si128((const __m128i*)index_gather_0);    
      // ... 
      // ... 
      // ... 
    // (7) initialize result temporary variable

    for(j = 0;j < (n);j += 1) {
      // (8) Load EPJ variable part
         xj_tmp_v0 = _mm256_set1_pd(xj[j][0]);
         xj_tmp_v1 = _mm256_set1_pd(xj[j][1]);
         xj_tmp_v2 = _mm256_set1_pd(xj[j][2]);
        // ... 
        // ... 
        // ...

      // (9) calculate interparticle
    }

    // (10) Store result part

  }
  return 0;
}
\end{lstlisting}
